Assessing rigor and impact of research software for hiring and promotion in psychology: A comment on Gärtner et al.~(2022)

### 2023-10-04 manuscript.Rmd
move roles from frontmatter to end

author: 
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,2,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Rüdesheimer Str. 50, 14197 Berlin"
    email         : "andreas.brandmaier@medicalschool-berlin.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Supervision"
  - name          : "Maximilian Ernst"
    affiliation   : "2,4"
    role:
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Aaron Peikert"
    affiliation   : "2,3,4"
    role:
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

@@

Explain the contribution of each authors. If you are the single author, please spell it out anyway for future proper credit of your contributions and meta-science studies. 
The Contributor Roles Taxonomy can be helpful. https://www.casrai.org/credit.html 
Please explain how the author names order connects to the contribution (e.g. alphabetical, ranked, or random order).

>>>>

author: 
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,2,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Rüdesheimer Str. 50, 14197 Berlin"
    email         : "andreas.brandmaier@medicalschool-berlin.de"
  - name          : "Maximilian Ernst"
    affiliation   : "2,4"
  - name          : "Aaron Peikert"
    affiliation   : "2,3,4"

@@

The authors made the following contributions.
Andreas M. Brandmaier: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing, Supervision;
Maximilian Ernst: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing;
Aaron Peikert: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing.
